\section{Tech log}

October Tasks

\begin{itemize}
        \item store alerts in supabase for further analysis later? Probably not.
        \item desktop app for spacy ner (published via hugginspace)
        \item post market report with similar methodology
        \item export more content from openbb where possible, recession indicator in weekly report?
        \item summarize bloomberg and yahoo finance results, pull data from remote csvs.
\end{itemize}

September Tasks

\begin{itemize}
    \item Finish off spacy ner with publishing and use it everywhere
    \item improve recommendation engine for parsing and suggesting results, store results in supabase for further analysis
    \item possible todo similar analysis to fdrtt constant calls and scrapping 24/7 via recalls.
    \item grab latest entries, idk wtf recommendation engine is doing. 
\end{itemize}

US 4434
CAD 566

About 88\% of entries are from the us, so removing that will cut the number of things I review by a lot.

Notes of what I have done tech related

\begin{itemize}
    \item Can extract stock comments
    \item extract livestream contents, light nlp application
    \item extract earning events from yahoo finance via spacy
    \item ner extraction via spacy
    \item contents of youtube videos via ytube nlp with static site search via pagefind
    \item attempts at algo trading, adapt to scan for price movements based on news to see if I missed something in the market, use postgres (supabase, to track these events)
    \item daily reports via datapane, could update this to make pdf and python web.
\end{itemize}